Carbonate chemistry at Ny-Ålesund

### 2021-05-05 awipev-CO2.Rmd
nothing

## Stratification
```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
# we look at the distribution of data
tmp <- d_all %>% 
  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
  group_by(month)

depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

>>>>

## Stratification
```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
# we look at the distribution of data
tmp <- d_hour %>% 
  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
  dplyr::mutate(month=month(d_hour$date, label = TRUE)) %>% 
  group_by(month)
depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::mutate(depth_group = depth_group_pressure) %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  group_by(depth_group, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  scale_x_discrete(labels = depth_labels) +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
